Forecasting the old-age dependency ratio to determine a sustainable pension age

### 2020-09-20 PensionAge.Rmd
Fixed heading of reproducibility section
Minor fixes

---
title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Shanghai, China
- familyname: Shang
  othernames: Han Lin
  address: Macquarie University, Sydney, Australia
abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population. Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
keywords: "coherent forecasts, demographic components, functional time series, pension age"
wpnumber: no/yr
jelcodes: J11,J14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \usepackage{todonotes, xcolor}
---

@@

# Sustainable pension age schemes

@@

## Finding the target pension age scheme {#sec:target}

@@

## Reproducibility {-}

>>>>

---
title: "Forecasting the old-age dependency ratio to determine a sustainable pension age"
author:
- familyname: Hyndman
  othernames: Rob J
  address: Department of Econometrics & Business Statistics\newline Monash University, Clayton VIC 3800, Australia
  email: Rob.Hyndman@monash.edu
  correspondingauthor: true
- familyname: Zeng
  othernames: Yijun
  address: Shanghai, China
- familyname: Shang
  othernames: Han Lin
  address: Macquarie University, Sydney, Australia
abstract: "We forecast the old-age dependency ratio for Australia under various pension age proposals, and estimate a pension age scheme that will provide a stable old-age dependency ratio at a specified level. Our approach involves a stochastic population forecasting method based on coherent functional data models for mortality, fertility and net migration, which we use to simulate the future age-structure of the population. Our results suggest that the Australian pension age should be increased to 68 by 2030, 69 by 2036, and 70 by 2050, in order to maintain the old-age dependency ratio at 23%, just above the 2018 level. Our general approach can easily be extended to other target levels of the old-aged dependency ratio and to other countries."
keywords: "coherent forecasts, demographic components, functional time series, pension age"
wpnumber: no/yr
jelcodes: J11,J14,C22
blind: false
cover: true
toc: false
bibliography: pensionage.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
---

@@

# Sustainable pension age schemes {#sec:target}

@@

## Finding the target pension age scheme

@@

# Reproducibility {-}
